Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest

### 2019-09-18 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
-Erika should be coauthor
-drafted first paragraph of intro.

---
title: "Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [book.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

@@

### Introduction
Understanding how and why trees respond to drought is critical to predicting forest drought responses and climate change feedbacks. (1 paragraph on this- I have lots of content on this and will add later.)

>>>>

---
title: "Tree size, microhabitat, and hydraulic traits shape drought responses in a temperate broadleaf forest"
author: "Ian McGregor, Ryan Helcoski, Norbert Kunert, Alan Tepley, Valentine Herrmann, Erika Gonzalez-Akre, Joseph Zailaa, Atticus Stovall, Norman Bourg?, William McShea?, Neil Pederson, Lawren Sack, Kristina Anderson-Teixeira"
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
bibliography: [book.bib,  packages.bib]
biblio-style: apalike
csl: apa.csl
header-includes:
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{caption}
- \captionsetup[table]{font=small}
- \captionsetup[figure]{font=small}
- \captionsetup[table]{labelformat=empty}
- \captionsetup[figure]{labelformat=empty}
- \usepackage{dcolumn} #for sidewaystable
---

@@

### Introduction
Forests globally play a critical role in climate regulation ([Bonan 2008](https://science.sciencemag.org/content/320/5882/1444)), yet there remains enormous uncertainty as to how the terrestrial carbon (C) sink, which is dominated by forests, will respond to climate change ([Friedlingstein et al. 2006](https://journals.ametsoc.org/doi/full/10.1175/JCLI3800.1)). An important aspect of this uncertainty lies in responses to drought (**REF**). In many forested regions around the world, the risk of severe drought is increasing ([Trenbert et al. 2014](https://www.nature.com/articles/nclimate2067)), even in conjunction with increasing precipitation ([IPCC 2014](https://www.cambridge.org/core/books/climate-change-2014-impacts-adaptation-and-vulnerability-part-b-regional-aspects/036A899BD52861D61B0D519C5F2B9334)). Global change-type drought has been affecting forests worldwide ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001)), and it is expected that future climate change-driven droughts will severely impact forests around the world ([Allen et al. 2015](https://doi.org/10.1016/j.foreco.2009.09.001); **REFS**). Larger trees tend to suffer more (e.g., [@bennett_larger_2015]; Stovall et al. 2019), resulting in disproportionate impacts on forest C storage ([Meakem et al. 2018](https://nph.onlinelibrary.wiley.com/doi/10.1111/nph.14633)). [Yet, modeling forest responses to drought remains challenging-- in part because some of the mechanisms underlying drought responses remain unclear.]
